Keyphrase Extraction from User Generated Content on Medical Domain

### 2017-05-23 sample-sigconf.tex
Add several formula
Add formula, contoh, dan tabel
Cut introduction
Nambahin bgian feature dan benerin skenario
Change Conclusion

\title{SIG Proceedings Paper in LaTeX Format}
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
The tremendous amount of user-generated contents, such as the questions about symptoms and diseases being asked by a user in online forums, or blog posts about dietary and fitness, are potential sources for enriching knowledge in medical document retrieval and health-related text mining applications. Understanding those various contents is simply not a trivial task. Reducing the complex characteristics of contents, including but not limited to linguistic variations, into structured information can help the text interpretation process. A common approach is to extract medical terms from each document using available tools, such as medical entity recognizer. However, we argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information. Hence, we use keyphrases extraction techniques to extract more important information about the concept of the document. Previous works in keyphrases extraction mostly focused on a general domain, long and formal written documents. These methods perform poorly when being applied to user-generated contents and medical documents. In this work, we propose deep bi-directional recurrent network and convolutional neural network as a model for extracting keyphrases. Furthermore, we leveraged word embedding, medical concepts from a knowledge base, and linguistic components as our features. The proposed algorithm achieved F1 score of 82.41\%. This result outperforms state of the art system for extracting keyphrases using a statistical model.
\end{abstract}

@@

\keywords{ACM proceedings, \LaTeX, text tagging}

@@

\end{document}

>>>>

\title{Keyphrase Extraction from User Generated Content on Medical Domain}
\iffalse
\titlenote{Produces the permission block, and
  copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}
\fi

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{F. Ilham et al.}

\begin{abstract}
The tremendous amount of user-generated contents, such as the questions about symptoms and diseases being asked by a user in online forums, or blog posts about dietary and fitness, are potential sources for enriching knowledge in medical document retrieval and health-related text mining applications. Understanding those various contents is simply not a trivial task. Reducing the complex characteristics of contents, including but not limited to linguistic variations, into structured information can help the text interpretation process. We argue that there are many missing pieces of information when we rely only on medical entities or keywords as main information. Hence, we use keyphrases extraction techniques to extract more important information about the concept of the document. Previous works in keyphrases extraction mostly focused on a general domain, long and formal written documents. These methods perform poorly when being applied to user-generated contents and medical documents. In this work, we propose deep bi-directional recurrent network and convolutional neural network as a model for extracting keyphrases. Furthermore, we leveraged word embedding, medical concepts from a knowledge base, and linguistic components as our features. The proposed algorithm achieved F1 score of 82.41\%. This result outperforms state of the art system for extracting keyphrases using a statistical model.
\end{abstract}

@@

\keywords{keyphrase extraction, health-related text mining, deep learning, recurrent neural networks, convolutional neural networks}

@@

\end{document}
\grid

### 2017-05-23 samplebody-conf.tex
Change Conclusion

	Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}. Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}. Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas. bagaimana penanggulangannya saat kambuh? terima kasih sblumnya dok. \\\\
	(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}. And when the symptom occur it's \textbf{very hurt when breathing}. Last week i fainted because cannot hold the pain when i was breathing. How is the treatment when it's occur? thanks before \\

@@

In this work, we view our problem as a sequence labeling task. That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities \\$P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ \\where $l$ is a small number.
\subsection{FEATURES}
Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well. As a result, we leveraged nine handcrafted features that can help our model to characterize sequence of keyphrases. Formally, our feature functions is, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.

@@

\subsection{Other Analysis}
We performed an error analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example "headache on (sakit kepala pada)", "medicine for (obat untuk)". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our knowledge base. Moreover, there are also special case for keyphrases like "treatment for headache and sore throat (penyembuhan untuk sakit kepala dan tenggorokan)", that keyphrase need to be captured as whole because "sore throat" have a connection with the word "treatment". But our model, failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.
\section{Conclusion}
We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach. We leverage a deep learning approach using CNN and B-LSTM. Moreover, we also extracted nine features that capture medical concepts from a knowledge base, and linguistic components as our features. With this model and features, we are able to overcome problems such as informal language, short document, and medical domain specific. Our model achieves F1 score of 82.41\% on manually annotated Indonesian medical questions.

@@

Furthermore, we realized that there are no solid evaluation method for keyphrase extraction. Partial evaluation may handle how the model extract sequences in a document. However, weights for importance in sequences are different between words. For example "therapy for pregnancy", in that keyphrase we may realize that "pregnancy" is more important than other words. Thus partial evaluation failed to capture that problem.

>>>>

	\texttt{Dok , saya sering sekali merasa \textbf{kram pada perut kanan bagian atas} disertai \textbf{detak jantung yang cepat} serta \textbf{keringat dingin} dan \textbf{pusing}. Dan saat kambuh seperti itu, \textbf{nafas sangat sakit}. Seminggu yang lalu sampai terkapar karena tidak kuat menahan sakitnya saat bernafas. bagaimana penanggulangannya saat kambuh? terima kasih sblumnya dok. \\\\
	(Doc, i frequently feel a \textbf{cramp on upper right stomach} with \textbf{fasten heart beat} also \textbf{cold sweat} and \textbf{headache}. And when the symptom occur it's \textbf{very hurt when breathing}. Last week i fainted because cannot hold the pain when i was breathing. How is the treatment when it's occur? thanks before)}

@@

In this work, we view our problem as a sequence labeling task. That is, given a medical question containing $N$ words $w = (w_1, w_2,...,w_N$, we want to find the best sequence pf labels $y = (y_1, y_2,..., y_N)$, in which each label is determined using probabilities \\$P(y_i|w_{i-l},...,w_{i+l},y_{i-l},...,y_{i+l})$ \\where $l$ is a small number.

Because we have a small dataset, our model would have a small learning material and an end-to-end learning approach will not work well. As a result, we leveraged nine handcrafted features that can help our model to characterize sequence of keyphrases. Formally, our feature functions is, $f_1, f_2, ..., f_9$, which map a word to a particular feature value.

@@

\subsection{Other Analysis}
We performed an error analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example "headache on (sakit kepala pada)", "medicine for (obat untuk)". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our knowledge base. Moreover, there are also special case for keyphrases like "treatment for headache and sore throat (penyembuhan untuk sakit kepala dan tenggorokan)", that keyphrase need to be captured as whole because "sore throat" have a connection with the word "treatment". But our model, failed to capture that connection, it extracted "treatment for headache" and "sore throat" separately.

\section{Conclusion}
We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain. Extracting information patient intentions and needs on user-generated medical content is not a trivial task due to the fact that the content are usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text. Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm. Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing. Although our model outperforms baseline models, further improvements are needed especially in evaluation method which cannot cover the whole problem.
\iffalse
We investigate a keyphrase extraction problem especially in Indonesian medical questions domain with sequence labeling approach. We leverage a deep learning approach using CNN and B-LSTM. Moreover, we also extracted nine features that capture medical concepts from a knowledge base, and linguistic components as our features. With this model and features, we are able to overcome problems such as informal language, short document, and medical domain specific. Our model achieves F1 score of 82.41\% on manually annotated Indonesian medical questions.

@@

Furthermore, we realized that there are no solid evaluation method for keyphrase extraction. Partial evaluation may handle how the model extract sequences in a document. However, weights for importance in sequences are different between words. For example "therapy for pregnancy", in that keyphrase we may realize that "pregnancy" is more important than other words. Thus partial evaluation failed to capture that problem.
\fi
